### 2014-03-17 src/analysis.Rnw
Fix graphs so that it makes sense

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + #facet_wrap(~type) +
  myopts +
  #xlab(label=expression(frac(all,sample))) +
  xlab(label=expression(all%/%sample)) +
  ylab('reduction') +
  #theme(legend.position="none") +
  opts(title="sample(x)")
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Original set $R^2 > 0.90$.}
\label{fig:powerplot}
\end{figure*}

@@

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              ifelse(grepl('per_op',operator), 'x% operator',
              'operator selection'))))))))
df$sampling <- with(df,
          ifelse(grepl('onelement',strategy), 'one(x)',
            ifelse(grepl('locelement',strategy), 'lines(x)',
              ifelse(grepl('withinelement',strategy), 'one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
'other')))))))

df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))

#ggplot(df, aes(mutant.reduction, sd.reduction)) +
#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
   geom_point(aes(shape=sampling, color=type)) + myopts
@
\caption{The mean reduction of mutants vs its standard deviation. Original set, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ is shown here. }
%\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here. }
\label{fig:fullimgsize}
\end{figure*}

>>>>

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + #facet_wrap(~type) +
  myopts +
  #xlab(label=expression(frac(all,sample))) +
  xlab(label=expression(all%/%sample)) +
  ylab('reduction') +
  #theme(legend.position="none") +
  opts(title="sample(x)")
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Original set $R^2 > 0.90$. Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e project is better}
\label{fig:powerplot}
\end{figure*}

@@

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)

df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              ifelse(grepl('per_op',operator), 'x% operator',
              'operator selection'))))))))
df$sampling <- with(df,
          ifelse(grepl('onelement',strategy), 'one.per.elem(x)',
            ifelse(grepl('locelement',strategy), 'num.lines(x)',
              ifelse(grepl('withinelement',strategy), 'within.one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
                      ifelse(grepl('xop',strategy), 'op.x%(x)',
                        ifelse(grepl('opsel',strategy), 'opsel(x)',
                          ifelse(grepl('^op$',strategy), 'op(x)',
'other'))))))))))

df <- subset(df, type!='block')
df <- subset(df, sampling %in% c('sample(x)', 'num.lines(x)', 'one.per.elem(x)', 'op.x%(x)', 'opsel(x)'))
df$sampling <- factor(df$sampling,levels=c('sample(x)', 'num.lines(x)', 'one.per.elem(x)', 'op.x%(x)', 'opsel(x)'))
#df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))
df$type <- factor(df$type, levels=c('line','method','class','project','x% operator','operator selection'))

#ggplot(df, aes(mutant.reduction, sd.reduction)) +
#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(shape=sampling, color=type)) + myopts
   geom_point(aes(shape=sampling, color=type),
   #position=position_jitter(width=0.1, height=0.1),
   size=3) +
   myopts +
   scale_color_manual(values = c('orange', 'purple', 'brown', 'red','blue', 'black'))
   # block scale_color_manual(values = c('brown','orange', 'purple', 'green', 'red','blue', 'black'))
   #theme(legend.position=c(0,1) ,legend.justification=c(0,1))
@
\caption{The mean reduction of mutants vs its standard deviation. Original set, main variations of sampling, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ are shown here. Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction}
%\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here. }
\label{fig:fullimgsize}
\end{figure*}
